\section{Adjointness}
\renewcommand{\hom}[1]{\rm{Hom}(#1)}
\begin{notation}
    Let $R$ be a ring. We work in $R$-mods.
\end{notation}
\proposition[]{
    Let $A\stackon{$f$}{\to} B \stackon{$g$}{\to} C$.
    Then if $\hom{C,M} \ \stackon{$(-)\circ g$}{\to} \ \hom{B,M} \ \stackon{$(-)\circ f$}{\to} \ \hom {A,M}$ is exact, the original sequence is exact too.
}
\begin{proof}
    Let $a\in A$. Then pick $M=B/f(a)=B'$, and consider the quotient map $(B\stackon{$\pi$}{\to} B') \in \hom{B,B'}$. Then $\pi \circ f \equiv 0$. So we have a lift $\pi':C\to B'$.
\[\begin{tikzcd}
	& C \\
	B & {B'} & {B/f(A)}
	\arrow["{\pi'}", dashed, from=1-2, to=2-2]
	\arrow["{g}",from=2-1, to=1-2]
	\arrow["\pi"', from=2-1, to=2-2]
	\arrow["{=}"{description}, draw=none, from=2-2, to=2-3]
\end{tikzcd}\]

    But then this means $\pi$ factors through $\rm{ker}(g)$. So that $\rm{Im} (f)\supseteq \rm{ker}(g)$.



    For the other inclusion, take $M=C$. The identity from $C\to C$ maps to $g\circ f$ becomes zero by exactness.  
\end{proof}

\begin{aproposition}{assigned as exericse}{contraexact}
    The contravariant functor $\hom{-,N}$ sends right exact sequences to left exact sequences.
\end{aproposition}
\begin{proof}
     Let $A\stackon{$f$}{\to} B \stackon{$g$}{\to} C \to 0$. We want \[
     0\to \hom{C,N} \to \hom{B,N}\to \hom{A,N}
     \]
     exact.
    Let $\alpha:C\to N$. Because $g$ is an epimorphism (surjective) we have for $\alpha\circ g=0=0\circ g \implies \alpha=0$. So we have exactness at $\hom{C,G(M)}$.

    For the exactness at $B$, the composite is zero from $g\circ f=0$. This gives one inclusion. Now let $\alpha:B\to N$ such that $\alpha\circ f=0$. Then $\rm{ker}(g)=\rm{Im}(f)\subseteq \rm{ker}(\alpha)$. By the mapping property of quotients we have a lift
\[\begin{tikzcd}
	B & {B/\rm{ker}(g)} & C \\
	& M
	\arrow["g", from=1-1, to=1-2]
	\arrow["\alpha"', from=1-1, to=2-2]
	\arrow["{=}"{description}, draw=none, from=1-2, to=1-3]
	\arrow[dashed,from=1-2, to=2-2]
\end{tikzcd}\]

\end{proof}
Similarly we have the same statement for the covariant functor
\begin{aproposition}{assigned as exericse}{}
      In $R$-mod, $A\stackon{$f$}{\to} B \stackon{$g$}{\to} C$ is exact if $\hom{N,A}\to \hom{N,B} \to \hom{N,C}$ is exact for all $N$.


\end{aproposition}
\begin{proof}
    For the first inclusion, take $N=A$, so then we have $g\circ f =0$ by considering the identity from $A\to A$. Now we want $\rm{ker} \ g \subseteq \rm{im} \ f$. Pick $N=\rm{ker} \ g$. Then the composite $N\to B \to C$ is zero, so has a lift $N\to A\to B \to C$.
    \[\begin{tikzcd}
	& {\rm{ker} \ g} \\
	A & B & C
	\arrow[dashed, from=1-2, to=2-1]
	\arrow[hook, from=1-2, to=2-2]
	\arrow[from=2-1, to=2-2]
	\arrow[from=2-2, to=2-3]
\end{tikzcd}\] But this is a lift of the embedding of $\rm{ker } \ g $ into $B$, so the kernel of $g$ is a subset of the image of $f$.
\end{proof}
\begin{aproposition}{assigned as exercise}  {coexact}
    The covariant functor $\hom{N,-} $ sends left exact sequences to left exact sequences. 
\end{aproposition}
\begin{proof}
     Let $0\to A\stackon{$f$}{\to} B \stackon{$g$}{\to} C$. We want \[
     0\to \hom{N,A} \to \hom{N,B}\to \hom{N,C}
     \]
     exact.
     Because $f$ is injective, this is an monomorphism so we have $\hom{N,A}\to \hom{N,B}$ injective. This gives exactness at $\hom{N,A}$.

     For exactness at $B$, we have that the composition $g\circ f=0$, so that gives one inclusion. For the other inclusion, let $N\stackon{$h$}{\to} C$ such that $g\circ h =0$. Then $\rm{Im} \ h\subseteq \rm{ker}\ g = \rm{Im} \ f$. $f$ is injective, so we can identify $\rm{Im} \ f$ with its preimage in $A$. This gives us a factoring of $h$ through $\rm{Im} \ f $ in $A$.
\end{proof}
\definition[]{Adjoint}{
    Let $\mathcal{C},\mathcal{D}$ categories. Let $F:\mathcal{C}\to \mathcal{D}$ and $G:\mathcal{D}\to \mathcal{C}$ functors. We say $F$ is a left adjoint of $G$ and $G$ is a right adjoint of $F$ if \[
        \hom{F(x),y} \quad \stackon{natural isom.}{\simeq} \quad \hom{x,g(y)}
    \]
}\begin{remark}
    As a recall natural isomorphism means that for every pair $(x,y)\in \mathcal{C}\times \mathcal{D}$ there is an isomorphism  $\eta_{x,y}\in \rm{Hom}_{\rm{Set}}{\hom{F(x),y},\hom{x,G(y)}}$ such that the following square commutes for every pair of morphisms $(f,g) \in \rm{Hom}_{\mathcal{C}}(x_1,x_2)\times \rm{Hom}_{\mathcal{D}}(y_1,y_2)$
    \[\begin{tikzcd}
	{\rm{Hom}_{\mathcal{D}}(F(x_1),y_1)} && {\rm{Hom}_{\mathcal{D}}(F(x_2),y_2)} \\
	{\rm{Hom}_{\mathcal{C}}(F(x_1),y_1)} && {\rm{Hom}_{\mathcal{C}}(F(x_2),y_2)}
	\arrow["{\rm{Hom}_{\mathcal{D}}(F(f),g)}", from=1-1, to=1-3]
	\arrow["{\eta_{x_1,y_1}}"', from=1-1, to=2-1]
	\arrow["{\eta_{x_2,y_2}}", from=1-3, to=2-3]
	\arrow["{\rm{Hom}_{\mathcal{C}}(f,G(g))}"', from=2-1, to=2-3]
\end{tikzcd}\]
\end{remark}
\theorem[]{}{
    In the setting of $R$-Mods, $S$-Mods,
    let $F, G$ adjoints. Then $G$ is left exact and $F$ is right exact. 
}\begin{proof}
    $F$ is right exact:
    Let $A\stackon{$f$}{\to} B \stackon{$g$}{\to} C\to 0$. We want $F(A)\to F(B)\to F(C)\to 0$ exact, so want to show that \[
   0 \to \hom{F(C),M}\to \hom{F(B),M}\to \hom{F(A),M}    \]
    exact for every $M\in \mathcal{D}.$

    By adjointness, this is equivalent to saying that 
    \[
    0 \to \hom{C,G(M)}\to \hom{B,G(M)}\to \hom{A,G(M)}  \] is exact for every $M$. But this is a direct result of (let $N=G(M)$) the (left) exactness of the functor $\hom{-,N}$.

    For the left exactness of $G$, we want \[
    0\to G(A)\to G(B)\to G(C)
    \] exact, so we want to show exactness of \[\begin{tikzcd}
	0 & {\rm{Hom}(N,G(A))} & {\rm{Hom}(N,G(B))} & {\rm{Hom}(N,G(C))} \\
	0 & {\rm{Hom}(F(N),A)} & {\rm{Hom}(F(N),B)} & {\rm{Hom}(F(N),C)}
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-2, to=1-3]
	\arrow["\simeq", from=1-2, to=2-2]
	\arrow[from=1-3, to=1-4]
	\arrow["\simeq", from=1-3, to=2-3]
	\arrow["\simeq", from=1-4, to=2-4]
	\arrow[from=2-1, to=2-2]
	\arrow[from=2-2, to=2-3]
	\arrow[from=2-3, to=2-4]
\end{tikzcd}\]
Which is true by the left exactness of the covariant functor.
\end{proof}
